Learning and Evaluation of \strips\ Action Models with Classical Planning

### 2018-05-31 doc/aij18/motivation.tex
small updates to sections 1,2,3

The main novelty of \FAMA with respect to other approaches lies in that our system is capable of handling \PO and \NO action sequences, which makes the learning task more challenging. Essentially, this brings two key differences: a) the transition function between two observed states may now involve more than one action; i.e., $\theta(s_i,\tup{a_1,\ldots,a_n})=s_{i+1}$; and b) the horizon of the input plan traces is not longer known. These two factors justify the use of planning techniques for solving the learning task over other methods such as a SAT solver.

>>>>

The main novelty of \FAMA with respect to other approaches lies in that our system is capable of handling \PO and \NO action sequences, which defines a more challenging learning task. Essentially, this brings one key difference:
\begin{itemize}
\item The transition between two given observed states may now involve the execution of more than one action; formally this means that $\theta(s_i,\tup{a_1,\ldots,a_k})=s_{i+1}$ where $k$ is unkown; The horizon of the input plan traces is not longer known what justify the use of planning techniques for solving the learning task over other methods such as a SAT solver. 
\end{itemize}
